\chapter{Requirements specification}

\section{Functional Requirements}
\begin{enumerate}

	\item The game must cater for users who are currently at level 2 of keystage 2 mathematics.
	\begin{enumerate}[label={1.\arabic*},nolistsep,leftmargin=*]
		\item There must be a puzzle in the game which challenges the users knowledge of subtraction facts up to 10.
		\item There must be a puzzle in the game which challenges the users knowledge of number ordering from 0 - 100.
		\item There must be a puzzle in the game which challenges the users knowledge of number sequencing. This must include odd and even numbers.
	\end{enumerate}

	\item The game must cater for users who are currently at level 3 of keystage 2 mathematics.
	\begin{enumerate}[label={2.\arabic*},nolistsep,leftmargin=*]
		\item There must be a puzzle in the game which challenges the users knowledge of the 2,3,4,5 and 10 times table.
		\item There must be a puzzle which forces a user to use multiplication or division to solve it. The multiplication or division must only be used with whole numbers. When choosing numbers for division numbers with remainders are to be included.	
		\item The game should include puzzles which involves breaking entities into simple fractions.
		\item Within the game there should be puzzles which require users to equate simple fractions.
	\end{enumerate}
	
		\item The game must cater for users who are currently at level 4 of keystage 2 mathematics.
		\begin{enumerate}[label={3.\arabic*},nolistsep,leftmargin=*]
			\item Puzzles must exist within the game which can only be solved using division by 10 or 100. The entities being divided must be whole numbers.
			\item A puzzle must exist which tests users upon their knowledge of multiplication facts up to 10x10. This puzzle should then go on to test whether the user can quickly derive correct divison facts.
			\item Within the game there should be a puzzle which involves adding and subtracting entities which represent decimal numbers to 2 decimal places.
			\item A puzzle should exist which forces the user to order decimal numbers. These decimal numbers can be up to three decimal places in length.
		\end{enumerate}
		
	\item Levels in the game must be constructed in such a way that each user contributes to a problem before all the users can progress. A user must contribute within the game physically.
	\item The game must not be single player and should allow players in groups of 3-4 to play together.
	\item The players should be able connect to dedicated servers to play the game.
	
	\item The mod must implement coins as one of the visual representations of numbers.
	
	\item The mod must have custom weapons which can be used to defeat zombies.
	
	\item Coins and other visual representations of numbers must be collected by defeating zombies.
	
	\item Zombies must not drop numbers or coins if the user does not defeat them using the specific mathematical weapon.
	
	\item Zombies must have a number above their head clearly visible to the player indicating what number they drop upon being defeated.
	
	\item Zombies should drop a number or coins equal to the number stated above the zombie's head.
	
	\item Players must be able to craft all mathematical operators using items collected throughout the level. (Mathematical operators being +,-,*,/) 
	
	\item Each mathematical operator must be represented visually in a way which is commonly understood by people of the specified age group.
	
	\item Puzzles must be solved in chambers as well as open world spaces.
	
	\item Players should not be allowed to progress until the puzzle they are currently on is completed.
	
	\item Mathematical operators must be usable objects and not weapons.
	
	\item Mathematical operators will be crafted using items which have been ascertained through resource collecting, where resource collecting is the action of getting items in any way but defeating zombies.
	
	\item Equations must be able to be crafted using mathematical operators and numbers collected from defeated zombies.
		
\end{enumerate}

\section{Non-Functional Requirements}
\begin{enumerate}
	\item The game must be implemented in Minecraft through a mod.
	\item The mod should work on Minecraft version 1.6.4.
	\item The mod must work on the windows operating system.
	\item The mod must work on a machine which has the minimum requirements of Minecraft or better.
	\item The game should abide by the ethics code in place within the education system for those between the ages of 8 and 11.
\end{enumerate}

